Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-21 main.tex
:pencil: Update algorithms

		\begin{algorithm}[!t]
			\caption{Numerical Evaluation of \gls{kkt} Input Distribution}
			\label{al:input_distribution}
			\begin{algorithmic}[1]
				\Require $K$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
				\State Set $\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
				\State \phantom{Set} $f(z|\mathcal{H}_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dtmac}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
				\State Get $P_{\mathcal{K}}^{(0)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
				\State \phantom{Get} $I^{(0)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
				\State \phantom{Get} $I^{(0)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
				\State \phantom{Get} $I^{(0)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
					\State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
					\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
					\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
					\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}

@@

				\State Get $(\sigma_{m_{\mathcal{K}}}^{(0)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
				\State \phantom{Get} $Q^{(0)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma} or \eqref{eq:regularized_incomplete_gamma_series}
				\State \phantom{Get} $I^{(0)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(0)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(0)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient}

@@

					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)} \gets \boldsymbol{w}^{(r-1)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r-1)}(x_{\mathcal{K}})$ \label{st:gradient_descent_begin}

@@

					\State \phantom{Update} $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
					\State \phantom{Update} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma} or \eqref{eq:regularized_incomplete_gamma_series}
					\State \phantom{Update} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}

@@

						\State Redo Step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end}

@@

>>>>

		\begin{algorithm}[!t]
			\caption{Numerical Evaluation of \gls{kkt} Input Distribution}
			\label{al:input_distribution}
			\begin{algorithmic}[1]
				\Require $K$, $N$, $\boldsymbol{h}_{\mathrm{D}}^H$, $\boldsymbol{H}_{\mathrm{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
				\State Set $\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
				\State \phantom{Set} $f(z|\mathcal{H}_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dtmac}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
				\State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
				\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information} \label{st:input_distribution_end}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
					% \State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
					% \State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
					% \State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
					% \State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information}
				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}

@@

				\State Get $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance} \label{st:gradient_descent_begin}
				\State \phantom{Get} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma} or \eqref{eq:regularized_incomplete_gamma_series}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient} \label{st:gradient_update_start}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient} \label{st:gradient_update_end}

@@

					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)} \gets \boldsymbol{w}^{(r-1)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r-1)}(x_{\mathcal{K}})$ \label{st:backtracking_line_search_begin}

@@

					\State Redo step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end} \label{st:backtracking_line_search_end}
					% \State \phantom{Update} $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
					% \State \phantom{Update} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma} or \eqref{eq:regularized_incomplete_gamma_series}
					% \State \phantom{Update} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:backtracking_line_search_end}

@@

						\State Redo step \ref{st:backtracking_line_search_begin}--\ref{st:backtracking_line_search_end}

@@

					\State Redo step \ref{st:gradient_update_start}, \ref{st:gradient_update_end}
